Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-16 main.Rmd
all figures are still interpretable in black and white.

(ref:allFig) Distribution of energy consumption displayed as letter value plots, illustrating harmonies and clashes, and how mappings change emphasis: **a** weekday/weekend faceted by quarter-of-year produces a harmony, **b** quarter-of-year faceted by weekday/weekend produces a harmony, **c** month-of-year faceted by quarter-of-year produces a clash, as indicated by the empty sets and white space. Placement within a facet should be done for primary comparisons. For example, arrangement in **a** makes it easier to compare across weekday type (x-axis) within a quarter (facet). It can be seen that in quarter 2, there is more mass occupied the lower tail on the weekends (letter value E with depth 1/8) relative to that of the weekdays (letter value D 1/16), which corresponds to more days with lower energy use in this period.

@@

In \autoref{fig:bothcust}b, the black line is the median, whereas the purple band covers the 25th to 75th percentile, the orange band covers the 10th to 90th percentile, and the green band covers the 1st to 99th percentile. The first facet represents the weekday behavior while the second facet displays the weekend behavior; energy consumption across each hour of the day is shown inside each facet. The energy consumption is extremely skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer compared to weekends.

>>>>

(ref:allFig) Distribution of energy consumption displayed as letter value plots, illustrating harmonies and clashes, and how mappings change emphasis: **a** weekday/weekend faceted by quarter-of-year produces a harmony, **b** quarter-of-year faceted by weekday/weekend produces a harmony, **c** month-of-year faceted by quarter-of-year produces a clash, as indicated by the empty sets and white space. Placement within a facet should be done for primary comparisons. For example, arrangement in **a** makes it easier to compare across weekday type (x-axis) within a quarter (facet). It can be seen that in quarter 2, there is more mass occupied the lower tail on the weekends (letter value E corresponding to tail area 1/8) relative to that of the weekdays (letter value D 1/16), which corresponds to more days with lower energy use in this period.

@@

In \autoref{fig:bothcust}b, the black line is the median, whereas the purple (narrow) band covers the 25th to 75th percentile, the orange (middle) band covers the 10th to 90th percentile, and the green (broad) band covers the 1st to 99th percentile. The first facet represents the weekday behavior while the second facet displays the weekend behavior; energy consumption across each hour of the day is shown inside each facet. The energy consumption is extremely skewed with the 1st, 10th and 25th percentile lying relatively close whereas 75th, 90th and 99th lying further away from each other. This is common across both weekdays and weekends. For the first few hours on weekdays, median energy consumption starts and continues to be higher for longer compared to weekends.
